Code Clones: To refactor or not to refactor?

### 2020-05-09 ase/paper.tex
Updates from Overleaf

% Experimental setup: how we validated that we fixed the problem
To conduct such refactorings in a controlled environment, we create a tool that can automatically refactor a set of duplication problems in Java source code. This set is selected because not all clones can easily be automatically refactored, so we define those that can. Using these definitions we can extract a sufficiently large dataset of refactored clones to perform our analyses. Our tool refactors 13k clones over 2k open-source Java projects and measures the delta maintainability scores of the refactoring.

@@

None of the surveyed tools had all the desired characteristics. Also, the output of these clone detection tools cannot be post-processed to match the clone definition proposed in Sec.~\ref{sec:research}. This is mainly because the automatically refactorable clones are not necessarily a subset of the clones detected by these tools (see Sec.~\ref{sec:different-types}) and will thus require an analysis of the entire system.

@@

% \subsection{Survey of existing clone detection tools}\label{sec:survey}
%To detect refactorable clones according to the definitions introduced in Sec.~\ref{sec:research}, we survey existing clone detection tools for their suitability.

%To detect clones that can be automatically refactored, we surveyed a set of modern clone detection tools and techniques~\cite{svajlenko2014evaluating, sheneamer2016survey, gautam2016various, roy2009comparison}. We created a set of control projects to determine the suitability of these tools to detect automatically refactorable clones, either through configuration or postprocessing of their output.

%None of the surveyed tools~\cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable for our definitions of refactorable clones, because of which we propose CR. This tool goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}. In the following sections, we explain these steps.

>>>>

% Experimental setup: how we validated that we fixed the problem
To conduct such refactorings in a controlled environment, we create a tool that can automatically refactor a set of duplication problems in Java source code. Because not all clones can easily be automatically refactored, we define those that can. Using these definitions we can extract a sufficiently large set of refactored clones to perform our analyses. Our tool refactors 13k clones over 2k open-source Java projects and measures the delta maintainability scores of the refactoring.

@@

None of the surveyed tools had all the desired characteristics. Also, the output of these clone detection tools cannot be post-processed to match the clone definition proposed in Sec.~\ref{sec:research}. This is because the automatically refactorable clones are not necessarily a subset of the clones detected by these tools (see Sec.~\ref{sec:different-types}) and will thus require an analysis of the entire system.

@@
